Harnessing the cloud to understand light: A whitepaper detailing the \MaxwellFDS core solver

### 2012-08-16 thesis.tex
Some updates.

\section*{Introduction}
\MaxwellFDS is a cloud-powered electromagnetic solver,
    tailored specifically to the field of nanophotonics.
\MaxwellFDS stands for Frequency-Domain Solver.

@@

\subsection{The advantages of simulating in the cloud}
The primary usefulness of the cloud in a simulation context
    is that it allows one to save both money and time.

@@

\subsection{The advantages of being built within Matlab}
\MaxwellFDS was designed to not only be scalable (in the cloud),
    but accessible as well.
For this reason, we have allowed

>>>>

\section*{Introduction}
\MaxwellFDS is a cloud-powered electromagnetic solver,
    tailored specifically to the field of nanophotonics.
\MaxwellFDS stands for Frequency-Domain Solver
    and delivers frequency-domain solutions to the electromagnetic wave equation
    directly to the Matlab programming environment,
    and does so in a scalable manner by harnessing the power
    of the Amazon Elastic Compute Cloud.

In this whitepaper, the core \MaxwellFDS solver is introduced.

@@

\subsection{The advantages of simulating in the cloud}
Although running scientific workloads in public cloud environments
    has not yet become the de facto standard,
    doing so provides many significant advantages.

@@

\subsection{The advantages of being built within Matlab}
The primary advantage of building \MaxwellFDS within Matlab is accessibility.

Often simulation packages are run as stand-alone programs
    which are controlled either by custom user interfaces
    or custom input and output file formats.
The result of this approach, however, is 
    \BI a steep learning curve for the user,
    \I  the need to create ``connection'' software
            in order to link the simulation package with
            the other packages or environments the user needs, and  
    \I  increased unreliablility, since the simulation software
            is inevitably less ``bullet-proof'' than standard
            platforms such as Matlab. \EI

For these reasons, the core solver of \MaxwellFDS is built
    \BI to resemble a simple Matlab command,
    \I  never requires the user to leave the Matlab environment
            (assuming the user has a valid Amazon Web Services ID). \EI

\MaxwellFDS was built with extreme simplicity in mind,
    so much so that its core solver is even contained in a single Matlab file,
